Shifting mutational effects on the evolutionary landscape of HIV Envelope

### 2017-11-25 paper/manuscript.tex
compute nearest distance to shifted / substituted sites
put shiftfeatures figure in paper

\author[1,2\authfn{1}]{Hugh K. Haddox}
\author[1,2\authfn{1}]{Adam S. Dingens}
\author[1,3]{Sarah K. Hilton}
\author[4]{Julie Overbaugh}
\author[1,2,3]{Jesse D. Bloom}
\affil[1]{Basic Sciences Division and Computational Biology Program, Fred Hutchinson Cancer Research Center, Seattle, WA}
\affil[2]{Molecular and Cellular Biology PhD program, University of Washington, Seattle, WA}
\affil[3]{Department of Genome Sciences, University of Washington, Seattle, WA}
\affil[4]{Human Biology Division, Fred Hutchinson Cancer Research Center, Seattle, WA}
\contrib[\authfn{1}]{These authors contributed equally to this work}

@@

\subsection*{Validating sites of mutational shifts}

@@

>>>>

\author[1,2,\authfn{1}]{Hugh K. Haddox}
\author[1,2,\authfn{1}]{Adam S. Dingens}
\author[1,3]{Sarah K. Hilton}
\author[4]{Julie Overbaugh}
\author[1,2,3]{Jesse D. Bloom}
\affil[1]{Basic Sciences Division and Computational Biology Program, Fred Hutchinson Cancer Research Center, Seattle, WA} 
\affil[2]{Molecular and Cellular Biology PhD program, University of Washington, Seattle, WA}
\affil[3]{Department of Genome Sciences, University of Washington, Seattle, WA}
\affil[4]{Human Biology Division, Fred Hutchinson Cancer Research Center, Seattle, WA}
\contrib[\authfn{1}]{These authors contributed equally to this work}

@@

@@

\begin{figure}
{\bf \Large A} \\
\includegraphics[width=0.9\textwidth]{figures/shifts_on_structure/shifts_on_structure.pdf}
\\
{\bf \Large B} \hspace{0.38\textwidth} {\bf \Large C} \hspace{0.28\textwidth} {\bf \Large D} \\
\includegraphics[width=0.4\textwidth]{figures/conservation_vs_shifts.pdf} 
\hspace{0.01\textwidth}
\includegraphics[width=0.28\textwidth]{figures/rsa_vs_shifts.pdf}
\hspace{0.01\textwidth}
\includegraphics[width=0.28\textwidth]{figures/shifts_proximity.pdf}
\caption{\label{fig:shiftfeatures}
CAPTION.
Note that the analyses in panels B-D are restricted to only those sites that are resolved in the Env crystal structure.
}
\figdata{Statistical testing of whether significantly shifted sites are more likely to have substituted between homologs are in \texttt{shifts\_vs\_subs\_table.txt}.}
\end{figure}

\begin{figure}
\centerline{\includegraphics[clip=true, trim=0in 0in 0in 0.7in, width=0.7\textwidth]{figures/entrenchment.pdf}}
\caption{\label{fig:entrenchment}
CAPTION
}
\end{figure}
